Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-07 draft.tex
almost there

Abstractly, we know that any algebra over the Swiss cheese operad can be modeled as a constructible factorization algebra on a manifold with boundary. 
One drawback of the previous section is that we did not provide a model for the $E_n$-center of an enveloping algebra as a constructible factorization algebra on an $(n+1)$-dimensional manifold with boundary. 
There is, however, a certain ``dequantization" of the $E_n$-center that we do have an explicit description of.

@@

Our first main result is the following.

@@

\begin{prp}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra 
\begin{equation}\label{eqn:graded}
\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
\end{equation}
on $M \times \RR_{\geq 0}$ such that $\pi_* {\bf Bulk}_n (\fg)$ is equivalent to ${\rm Gr} \; \bZ_n(\fg)$ as commutative factorization algebras on $M$ where $\pi : M \times \RR_{\geq 0} \to M$ is the projection.

\brian{lifts to $\PP_0$}.
\end{prp}

A $\PP_0$, or $1$-shifted Poisson, algebra is a commutative dg algebra equipped with a bracket of cohomological degree $+1$ that satisfies a graded version of the Jacobi identity and is a biderivation with respect to the commutative product \brian{reference}. 
Likewise, a $\PP_0$-factorization algebra is a factorization algebra whose value on each open set is $\PP_0$-algebra.

@@

Following the proof of this proposition, our main thrust is to interpret this result in the BV formalism by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is precisely the constructible factorization algebra in (\ref{eqn:graded}).

@@

\begin{prp}
Filtered swiss cheese.
Gr is a P_0 swiss cheese algebra.
\end{prp}

@@

For any dg Lie (in fact, $L_\infty$) algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
If $\fh$ is a dg Lie algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
The associated graded is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
\[
{\rm Gr} \; \clieu (\fh) = {\rm Sym} (\fh [1])  .
\]
Here, the differential on the right-hand side is simply the underlying linear differential of $\fh$ (in terms of $L_\infty$ algebras, this is the $1$-ary operation $\ell_1$).

@@

Consider our factorization model for the $E_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra. 
Furthermore, the resulting associated graded ${\rm Gr} \; \bU_n (\fg)$ has the natural structure of a $\PP_0$-factorization algebra.

There is a similar filtration on our model for the $E_n$-center $\bZ_n(\fg)$. 
Define
\[
F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]
It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.

@@

>>>>

Given an $E_n$-algebra $A$ the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $E_n$-enveloping algebra.

\begin{prp} \label{prp:swiss1}
Let $\fg$ be a Lie algebra. 
The pair $(\fZ_n(\fg) , \UU_n(\fg))$ is a filtered object in the $\infty$-category of algebras over the $(n+1)$-dimensional Swiss cheese operad. 
The resulting associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ is a commutative algebra object.
\end{prp}

@@

\brian{additivity}

\begin{rmk}
By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
\[
\clie \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
\]
is a model for the {\em $\PP_n$-center} of the $\PP_n$-enveloping algebra $\UU_{\PP_n} (\fg)$. 
\end{rmk}

The associated graded pair in Proposition \ref{prp:swiss1} carries the additional Poisson-type structure.

\begin{prp} \label{prp:poisson}
The associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ determines an algebra over the operad $\PP_{[n+1,n]}$. 
\end{prp}

There is another geometric picture for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
One drawback of the previous section is that we did not provide a model for the $E_n$-center of an enveloping algebra as a constructible factorization algebra on an $(n+1)$-dimensional manifold with boundary.

A constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a pair of factorization algebras $(\pi_* \bA , \bA_{\partial})$ on $M$ which locally define the $E_1$-model for $(n+1)$-Swiss cheese algebras.

The next goal of this section is to provide a model of the classical limit of the $E_n$-center as a constructible factorization algebra.

@@

\begin{prp}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ such that the pair 
\[
(\pi_* {\bf C}_n (\fg), {\bf C}_n (\fg)_\partial)
\]
is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as commutative factorization algebras \brian{adjectives}
\end{prp}

%A $\PP_0$, or $1$-shifted Poisson, algebra is a commutative dg algebra equipped with a bracket of cohomological degree $+1$ that satisfies a graded version of the Jacobi identity and is a biderivation with respect to the commutative product \brian{reference}. 
%Likewise, a $\PP_0$-factorization algebra is a factorization algebra whose value on each open set is $\PP_0$-algebra.

Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is precisely the constructible factorization algebra in (\ref{eqn:graded}).

@@

@@

@@

We accomplish Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $E_n$-center.

For any dg Lie (in fact, $L_\infty$) algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
If $\fh$ is a dg Lie algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
The associated graded cochain complex is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
\[
{\rm Gr} \; \clieu (\fh) = {\rm Sym} (\fh [1])  .
\]
Here, the differential on the right-hand side is simply the underlying linear differential of $\fh$ (in terms of $L_\infty$ algebras, this is the $1$-ary operation $\ell_1$).

@@

Consider our factorization model for the $E_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.

There is a similar filtration on our model for the $E_n$-center $\bZ_n(\fg)$. 
Define
\[
F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]

\brian{$\PP_0$ stuff}

The associated graded commutative factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ lift to $\PP_0$-factorization algebras.

\begin{prp}
The pair $(\bZ_n (\fg), \bU_n(\fg)$ is a filtered, \brian{not sure what we're calling this}. 
Further, the associated graded $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg)$ is a $\PP_0$ \brian{not sure what we're calling this}. 
\end{prp}

It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.

@@

It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.
